\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage{subcaption}
\usepackage{appendix}
\usepackage[a4paper, width=150mm, top=25mm, bottom=25mm]{geometry}
% \usepackage{fancyhdr}
\usepackage[section]{placeins}

% \pagestyle{fancy}
% \fancyhead[RO, LE]{Thesis Title}



\title{Thesis Title}
\author{Vishal Pandey}
\date{17th May 2020}

\pagenumbering{roman}

\begin{document}


\include{titlepage}

\include{declaration}
\addcontentsline{toc}{chapter}{\numberline{}Declaration}
\setcounter{page}{2}

\include{certificate}
\addcontentsline{toc}{chapter}{\numberline{}Certificate}
\setcounter{page}{3}

\include{acknowledgement}
\addcontentsline{toc}{chapter}{\numberline{}Acknowledgement}
\setcounter{page}{4}

\include{abstract}
\addcontentsline{toc}{chapter}{\numberline{}Abstract}
\setcounter{page}{5}

\listoffigures
\addcontentsline{toc}{chapter}{\numberline{}List of figures}
\setcounter{page}{6}

\listoftables
\addcontentsline{toc}{chapter}{\numberline{}List of tables}
\setcounter{page}{7}

\include{list-of-abbreviation}
\addcontentsline{toc}{chapter}{\numberline{}List of abbreviation}
\setcounter{page}{8}

\tableofcontents
\newpage
\pagenumbering{arabic}
\chapter{Introduction}
\input{chapters/introduction}

\chapter{Literature Survey}
\input{chapters/chapter02}

\chapter{Prelimnary Techniques}
\input{chapters/chapter03}

\chapter{Critical Analysis of Imputation Techniques}
\input{chapters/chapter04}

\chapter{Proposed Work}
\input{chapters/chapter05}

\chapter{Results and Analysis}
\input{chapters/results}

\chapter{Conclusion}
\input{chapters/conclusion}


\appendix
\chapter{Screenshots of Implementation}
\input{chapters/appendix}

\begin{thebibliography}{}

\bibitem{1}[M. Mousa, M. Abdulaal, S. Boyles and C. Claudel, "Wireless Sensor Network-Based Urban Traffic Monitoring Using Inertial Reference Data," 2015 International Conference on Distributed Computing in Sensor Systems, Fortaleza, 2015, pp. 206-207, doi: 10.1109/DCOSS.2015.21.

\bibitem{2}[H. Furtado and R. Trobec, "Applications of wireless sensors in medicine," 2011 Proceedings of the 34th International Convention MIPRO, Opatija, 2011, pp. 257-261.

\bibitem{3}[Bardella, A., Danieletto, M., Menegatti, E. et al. Autonomous robot exploration in smart environments exploiting wireless sensors and visual features. Ann. Telecommun. 67, 297–311 (2012). https://doi.org/10.1007/s12243-012-0305-z

\bibitem{4}[M. R. M. Kassim and A. N. Harun, "Applications of WSN in agricultural environment monitoring systems," 2016 International Conference on Information and Communication Technology Convergence (ICTC), Jeju, 2016, pp. 344-349, doi: 10.1109/ICTC.2016.7763493.

\bibitem{5}[@book{10.5555/1643457,
author = {Mao, Guoqiang and Fidan, Baris and Mao, Guoqiang and Fidan, Baris},
title = {Localization Algorithms and Strategies for Wireless Sensor Networks},
year = {2009},
isbn = {1605663964},
publisher = {Information Science Reference - Imprint of: IGI Publishing},
address = {Hershey, PA}
}

\bibitem{6}[J. Zhang, W. Li, Z. Yin, S. Liu and X. Guo, "Forest fire detection system based on wireless sensor network," 2009 4th IEEE Conference on Industrial Electronics and Applications, Xi'an, 2009, pp. 520-523, doi: 10.1109/ICIEA.2009.5138260.

\bibitem{7}[Susanto, Hengky \& Chang, Chorng \& Lalooses, Francine. (2007). AN APPROACH FOR TRACKING WILDLIFE USING WIRELESS SENSOR NETWORKS. 

\bibitem{8}[T. M. Thekkil and N. Prabakaran, "Real-time WSN based early flood detection and control monitoring system," 2017 International Conference on Intelligent Computing, Instrumentation and Control Technologies (ICICICT), Kannur, 2017, pp. 1709-1713, doi: 10.1109/ICICICT1.2017.8342828.

\bibitem{9}[R. Das, S. Ghosh and D. Mukherjee, "Bayesian Estimator Based Weather Forecasting using WSN," 2018 3rd International Conference and Workshops on Recent Advances and Innovations in Engineering (ICRAIE), Jaipur, India, 2018, pp. 1-4, doi: 10.1109/ICRAIE.2018.8710410.

\bibitem{10} https://www.electronicshub.org/wireless-sensor-networks-wsn/

\bibitem{11} Matin, M.A. \& Islam, M.M. Overview of Wireless Sensor Network; IntechOpen: London, UK (2012)

\bibitem{12} S. Sharma, R. K. Bansal and S. Bansal, "Issues and Challenges in Wireless Sensor Networks," 2013 International Conference on Machine Intelligence and Research Advancement, Katra, 2013, pp. 58-62, doi: 10.1109/ICMIRA.2013.18.

\bibitem{13} Palm G. (1986) Warren McCulloch and Walter Pitts: A Logical Calculus of the Ideas Immanent in Nervous Activity. In: Palm G., Aertsen A. (eds) Brain Theory. Springer, Berlin, Heidelberg

\bibitem{14} F. Q. Lauzon, "An introduction to deep learning," 2012 11th International Conference on Information Science, Signal Processing and their Applications (ISSPA), Montreal, QC, 2012, pp. 1438-1439, doi: 10.1109/ISSPA.2012.6310529.

\bibitem{15} https://www.oreilly.com/library/view/deep-learning/9781491924570/ch04.html

\bibitem{16} S. Albawi, T. A. Mohammed and S. Al-Zawi, "Understanding of a convolutional neural network," 2017 International Conference on Engineering and Technology (ICET), Antalya, 2017, pp. 1-6, doi: 10.1109/ICEngTechnol.2017.8308186.

\bibitem{17} T. Liu, T. Wu, M. Wang, M. Fu, J. Kang and H. Zhang, "Recurrent Neural Networks based on LSTM for Predicting Geomagnetic Field," 2018 IEEE International Conference on Aerospace Electronics and Remote Sensing Technology (ICARES), Bali, 2018, pp. 1-5, doi: 10.1109/ICARES.2018.8547087.

\bibitem{18} A. Pulver and S. Lyu, "LSTM with working memory," 2017 International Joint Conference on Neural Networks (IJCNN), Anchorage, AK, 2017, pp. 845-851, doi: 10.1109/IJCNN.2017.7965940.

\bibitem{19} Weiss, K., Khoshgoftaar, T.M. \& Wang, D. A survey of transfer learning. J Big Data 3, 9 (2016). https://doi.org/10.1186/s40537-016-0043-6

\bibitem{20} Bird, Jordan J.; Kobylarz, Jhonatan; Faria, Diego R.; Ekart, Aniko; Ribeiro, Eduardo P. (2020). "Cross-Domain MLP and CNN Transfer Learning for Biological Signal Processing: EEG and EMG". IEEE Access. Institute of Electrical and Electronics Engineers (IEEE). 8: 54789–54801. doi:10.1109/access.2020.2979074. ISSN 2169-3536

\bibitem{21} Kim, T., \& Kim, H. Y. (2019). Forecasting stock prices with a feature fusion LSTM-CNN model using different representations of the same data. PLOS ONE, 14(2), e0212320.

\bibitem{22} Kyunghyun Cho, Bart van Merri¨ enboer, Caglar Gulcehre, Dzmitry Bahdanau, Fethi Bougares, Holger Schwenk and Yoshua Bengio. Learning Phrase Represen-tations using RNN Encoder–Decoder for Statistical Machine Translation

\bibitem{23}  H. Verma and S. Kumar, “An accurate missing data prediction method using LSTM based deep learning for health care,” in Proc. 20th Int. Conf. Distrib. Comput. Netw., 2019, pp. 371–376

\bibitem{24} D. S. Fung. Methods for the estimation of missing values in time series. 2006.

\bibitem{25} A. C. Harvey. Forecasting, structural time series models and the Kalman filter. Cambridge university press, 1990.

\bibitem{26} M. J. Azur, E. A. Stuart, C. Frangakis, and P. J. Leaf. Multiple imputation by chained equations: what is it and how does it work? International journal of methods in psychiatric research, 20(1):40–49, 2011.

\bibitem{27} X. Yi, Y. Zheng, J. Zhang, and T. Li. St-mvl: filling missing values in geo-sensory time series data. 2016.

\bibitem{28} J. Wang, A. P. De Vries, and M. J. Reinders. Unifying user-based and item-based collaborative filtering approaches by similarity fusion. In Proceedings of the 29th annual international ACM SIGIR conference on Research and development in information retrieval, pages 501–508. ACM, 2006.

\bibitem{29} H. Yuan, G. Xu, Z. Yao, J.Jia, and Y.Zhang, “Imputation of missing data in time series for air pollutants using long short-term memory recurrent neural networks,” in Proc. ACM Int. Joint Conf. Int. Symp. Pervasive Ubiquitous Comput. Wearable Comput., 2018, pp. 1293–1300.

\bibitem{30} Z. Che, S. Purushotham, K. Cho, D. Sontag, and Y. Liu. Recurrent neural networks for multivariate time series with missing values. Scientific reports, 8(1):6085, 2018.


\bibitem{31}  Ilya Sutskever, Oriol Vinyals, and Quoc V. Le. 2014a. Sequence to sequence learning with neural networks. In Advances in Neural Information Processing Sys-tems 27: Annual Conference on Neural Information Processing Systems 2014, December 8-13 2014, Montreal, Quebec, Canada, pages 3104–3112.

\bibitem{32}C. Leke, B. Twala, and T. Marwala, “Missing data prediction and classiﬁcation: The use of auto-associative neural networks and optimization algorithms,” arXiv preprint arXiv:1403.5488, 2014

\bibitem{33} Kyunghyun Cho, Bart van Merri¨ enboer, Caglar Gulcehre, Dzmitry Bahdanau, Fethi Bougares, Holger Schwenk and Yoshua Bengio. Learning Phrase Represen-tations using RNN Encoder–Decoder for Statistical Machine Translation

\bibitem{34} Moghar, A., \& Hamiche, M. (2020). Stock Market Prediction Using LSTM Recurrent Neural Network. Procedia Computer Science, 170, 1168–1173. doi:10.1016/j.procs.2020.03.049 

% \bibitem{35} 

\bibitem{35}  Yang, Y., Guizhong, L.: Multivariate time series prediction based on neural networks applied to stock market. In: 2001 IEEE International Conference on Systems, Man and Cybernetics. e-Systems and e-Man for Cybernetics in Cyberspace (Cat. No. 01CH37236), vol. 4, IEEE (2001)

\bibitem{36} Zhang, G.P.: Time series forecasting using a hybrid ARIMA and neural network model. Neurocomputing 50, 159–175 (2003)

\bibitem{37}  J. Yang, M. N. Nguyen, P. P. San, X. Li, and S. Krishnaswamy, “Deep convolutional neural networks on multichannel time series for human activity recognition.” in Ijcai, vol. 15, 2015, pp. 3995–4001. 

\bibitem{38} Zhang, Y.-F., Thorburn, P., Xiang, W., \& Fitch, P. (2019). SSIM -A Deep Learning Approach for Recovering Missing Time Series Sensor Data. IEEE Internet of Things Journal, 1–1. doi:10.1109/jiot.2019.2909038 

\end{thebibliography}

\end{document}